An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 VLDB2026/main.tex
change challenge

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}

	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}

	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf}

	\end{minipage}
\end{figure*}

\begin{figure*}
	\centering
	\setlength{\abovecaptionskip}{0.0cm}
	\begin{minipage}[t]{0.37\textwidth}
		\centering
		\caption{Multi-Modal Datasets}
		\label{fig:attribute-multimodal}  
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.37\textwidth}
		\centering
		\caption{Different Platforms}
		\label{fig:attribute-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.24\textwidth}
		\centering
		\caption{Large-Scale Dataset}
		\label{fig:attribute big dataset}
	\end{minipage}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.7\textwidth]{figures/exp/range_legend.pdf}

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}

	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}

	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf}

	\end{minipage}

\end{figure*}

\begin{figure*}
	\centering
	\setlength{\abovecaptionskip}{0.0cm}
	\begin{minipage}[t]{0.37\textwidth}
		\centering
		\caption{Multi-Modal Datasets}
		\label{fig:range-multimodal} 
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.37\textwidth}
		\centering
		\caption{Different Platforms}
		\label{fig:range-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.24\textwidth}
		\centering
		\caption{Large-Scale Dataset}
		\label{fig: range big dataset}
	\end{minipage}
\end{figure*}

@@

\textcolor{violet}{Notably, we find that IVF-based methods are easily extendable to support joint query scenarios of attribute filtering and range filtering, and are compatible with arbitrary combinations of Boolean logic. Our experiments also indicate that IVF-based methods (CAPS, Puck) achieve performance comparable to graph algorithms, while having the lowest time and space overhead, making them highly suitable for large-scale data processing. Therefore, IVF-based hybrid query methods represent a very promising research direction.}

@@

%	Our experiments show that graph compression methods often lead to poor query performance in RF-ANN search. To address this problem, subsequent algorithms usually optimize the index processing at the segment tree nodes. UNIFY newly proposes segment graphs and integrates multiple data structures to process queries. Although UNIFY performs slightly worse on small-range queries, its proposed index structure broadens the research direction.

\textcolor{blue}{
Experimental results show that different algorithms exhibit varying strengths under different query ranges. Therefore, designing a general range query algorithm that can adapt to diverse query conditions holds significant research value. For example, UNIFY demonstrates strong generality by dynamically selecting execution strategies based on the query range. Building on this idea, further exploration of more adaptive and high-performance range query algorithms is a promising direction for future research.}

In our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement. We suggest future future range filtering algorithms include Faiss as a baseline.

>>>>

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
		\caption{Multi-Modal Datasets}
		\label{fig:attribute-multimodal} 
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
		\caption{Different Platforms}
		\label{fig:attribute-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
		\caption{Large-Scale Dataset}
		\label{fig:attribute big dataset}
	\end{minipage}
\end{figure*}

@@

	\includegraphics[width=0.7\textwidth]{figures/exp/range_legend.pdf}

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
		\caption{Multi-Modal Datasets}
		\label{fig:range-multimodal} 
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
		\caption{Different Platforms}
		\label{fig:range-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
		\caption{Large-Scale Dataset}
		\label{fig: range big dataset}
	\end{minipage}
\end{figure*}

@@

\textcolor{violet}{Notably, we find that IVF-based methods are easily extendable to support joint query scenarios of attribute filtering and range filtering, and are compatible with arbitrary combinations of Boolean logic. Experiments in this paper also indicate that IVF-based methods (CAPS, Puck) achieve performance comparable to graph algorithms, while having the lowest time and space overhead, making them highly suitable for large-scale data processing. Therefore, IVF-based hybrid query methods represent a very promising research direction.}

@@

\textcolor{blue}{
In addition,our experiments show that different algorithms exhibit varying strengths under different query ranges. Therefore, designing a general range query algorithm that can adapt to diverse query conditions holds significant research value. For example, UNIFY demonstrates strong generality by dynamically selecting execution strategies based on the query range. Building on this idea, further exploration of more adaptive and high-performance range query algorithms is a promising direction for future research.}

Moreover, in our experiments, many range filtering algorithms perform worse than Faiss at high recall (0.95), showing that current algorithm designs still need improvement. We suggest future future range filtering algorithms include Faiss as a baseline.
